\section{Assumptions and Notions}
\subsection{General Assumptions}
\begin{itemize}
	\item We mainly consider the consumption of fossil fuels, renewable energy and nuclear ernergy. At the same time, we consider the proportion of fossil fuels, renewable energy and nuclear energy.
	\item We do not consider energy loss such as the loss of  electricity system and co-product fuel ethanol when calculating renewable energy costs because of lack of price data.
	\item We assume that the electricity is often consumed in time, and the electricity stored in the battery will be consumed by the commercial sectoer.
	\item We do not take the electricity producted from fossil fuels into consideration because we do not know the efficiency of the conversion of various of fossil fuels into electricity.
	\item We consider various types of renewable energy,  nuclear energy will be converted into electricity.
	\item We approximate the sum of renewable energy production，electricity produced from nuclear energy，net imports of electricity into the United States and net interstate sales of electricity and associated losses (negative and positive values) as electricity total consumption.
	\item When considering the proportion of various of energy, we mainly focus on fossil fuel energy, renewable energy and nuclear energy because there is an overlap between electricity consumption and the energy described above.
	\item We ignore the impact of the world energy reserves and trade patterns.
\end{itemize}
%\usepackage[table]\{xcolor\} is necessary !
\subsection{Notations}
\begin{table}[h]
	\centering
	%\caption{Notations}
	\label{my-label}
	\begin{tabular}{@{}cl@{}}
		\toprule
		\multicolumn{1}{l}{Abbreviation} & Description                                                             \\ \midrule
		\textit{A}                       & Per capita GDP, is defined as the quotient of GDPRX over TPOPP          \\
		\textit{P(t)}                    & The proportion of certain types of energy at the end of year t          \\
		\textit{Q(t)}                    & The impact factor of certain types of sector at the end of year t       \\
		\textit{c(t)}                    & The fitting consumption of certain types of energy at the end of year t \\
		\textit{v(t)}                    & The growth rate of certain types of energy at the end of year t         \\
		\textit{rc(t)}                   & The real consumption of certain types of energy at the end of year t    \\
		\textit{TC(t)}                   & The consumption of total energy at the end of period t                  \\ \bottomrule
	\end{tabular}
\end{table}
