%% This is file `mcmthesis-demo.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% mcmthesis.dtx  (with options: `demo')
%% 
%% -----------------------------------
%% 
%% This is a generated file.
%% 
%% Copyright (C)
%%     2010 -- 2015 by Zhaoli Wang
%%     2014 -- 2016 by Liam Huang
%% 
%% This work may be distributed and/or modified under the
%% conditions of the LaTeX Project Public License, either version 1.3
%% of this license or (at your option) any later version.
%% The latest version of this license is in
%%   http://www.latex-project.org/lppl.txt
%% and version 1.3 or later is part of all distributions of LaTeX
%% version 2005/12/01 or later.
%% 
%% This work has the LPPL maintenance status `maintained'.
%% 
%% The Current Maintainer of this work is Liam Huang.
%% 
\documentclass{mcmthesis}
\mcmsetup{CTeX = false,   % 使用 CTeX 套装时，设置为 true
        tcn = \large 89307, problem = \Huge c,
        sheet = true, titleinsheet = true , keywordsinsheet = true,
        titlepage = false, abstract = false}
\usepackage{booktabs}    
\usepackage{multirow}
\usepackage{cases}
\usepackage{mathtools}
\usepackage{url}
\usepackage{palatino}
\usepackage{xcolor}
\usepackage{caption}
\usepackage{subfigure}
\usepackage{array}
\usepackage[framed,numbered,autolinebreaks,useliterate]{mcode}%引入matlab代码用
\setlength{\parindent}{0pt}
\setlength{\parskip}{18pt}
\usepackage{listing}
\usepackage{graphicx}%插入图片的宏包
\usepackage{epstopdf}%插入eps矢量图
\usepackage{xfrac}%插入斜分式
\usepackage[UTF8, nocap]{ctex}%显示中文
%\usepackage{fontspec}
%\setmainfont[Mapping=tex-text]{KaiTi}%楷体
\usepackage{ marvosym }%产生阴阳符号，真的神奇,注明是文本环境了
\usepackage{ wasysym }%产生电话符号用宏包
%\usepackage{hyperref}%产生目录超链接。，没有也有目录链接
\bibliographystyle{elsarticle-num}%参考了一份不太简短得到的
\renewcommand{\headset}{{\Large 2018}\\MCM/ICM\\ Summary Sheet}
\title{\textbf{A Four-State Energy Compact}}
%{The \LaTeX{} Template for MCM Version \MCMversion}
\author{\small Control Number: \#89307}
\date{\today}
\begin{document}
\begin{abstract}
Energy is an important support of modern economy. In our paper, we construct a model defining the four-state energy compact integrating variables to process data, and succeed in characterizing the engergy profile by proportion and growth rate.\\
First, we integrate variables and make engergy profile shown as an area chart. We develop Energy Profile Model composed of Energy Proportion Model and Growth Rate Model.To obtain the proportion of energy in each state over time, we further simplify variables to fossil fuels energy, renewable energy and nuclear energy. After using sinusoidal model to fit cures, we get the function expressions between prportion and time. We use Moving Average in Time Series to get 1963-2007 energy consumption. We establish Growth Rate Model in similar way.\\
Next, we choose sector (industry，commerce and
residential industries) and population to discuss influential factors of the similarities and differences about the four states’ usage of cleaner, renewable energy sources. Thus we define the impact factor.The similarity is that the ratio of impact factors of AZ, NM, TX is $ 3.412 : 1 : 1 $. We use the IPAT formula and the revised ”Laspeyres” exponential decomposition method to analyze the impact of population growth.\\
Then, we select the average price, import expenditure size and size of productivity of power as the evaluation criteria. And use analytical hierarchy process (AHP) to determine their weights. In 2009, Texas had the "best" have the “best” profile for use of cleaner, renewable energy whose total sort weight is 0.4043. We give two kinds of predictive values of the energy profile of each state for 2025 and 2050 based on two models.\\
Finally, we state that the average price of electricity should be set at about 28.26 dollars in 2025 and 34.97 dollars in 2050 as the goal for this new four-state energy compact.
We discuss three actions the four states might take to meet their energy
compact goals.
\begin{keywords}
Renewable Energy, IPAT, AHP, Time Series, Electricity
\end{keywords}
\end{abstract}
\maketitle
\tableofcontents
\include{memo}
\input{introduction}
\input{AssumptionsandNotions}
\input{energyprofilemodel}
\input{efficiencyofservicemodel}
%\input{sensitivityanalysis}
\input{strengths}
\input{Conclusion}
%\input{FutureWork}

\bibliography{mcm}
	
\begin{appendices}
	Program List\\
	1.The code used to make the area chart
	%\textbf{\textcolor[rgb]{0.98,0.00,0.00}{Input matlab source:}}
	\lstinputlisting[language=Matlab]{mcode/mianjituAZ.m}
	\lstinputlisting[language=Matlab]{mcode/mianjituCA.m}
	\lstinputlisting[language=Matlab]{mcode/mianjituNM.m}
	\lstinputlisting[language=Matlab]{mcode/mianjituTX.m}
	
	2.The code used to make the energy proportion curve
	\lstinputlisting[language=Matlab]{mcode/11nengyuanzhanbi.m}
	3.The code used to make the growth rate fit curve of energy
	\lstinputlisting[language=Matlab]{mcode/Fossilfuelconsumptiongrowthrate.m}
	\lstinputlisting[language=Matlab]{mcode/AZzhouzengzhangsudu.m}
	\lstinputlisting[language=Matlab]{mcode/CAzhouzengzhangsudu.m}
	\lstinputlisting[language=Matlab]{mcode/NMzhouzengzhangsudu.m}
	\lstinputlisting[language=Matlab]{mcode/TXzhouzengzhangsudu.m}
	4.The code used to make the growth rate fit curve of Fossil Fuels energy
	\lstinputlisting[language=Matlab]{mcode/Fossilfuelconsumptiongrowthrate.m}
	5.The code used to make the growth rate fit curve of Nuclear energy
	\lstinputlisting[language=Matlab]{mcode/Nuclearenergyconsumptiongrowthrate.m}
	6.The code used to make The impact factors of CA changes over time
	\lstinputlisting[language=Matlab]{mcode/hangyeyingxiang.m}
	7.The code used to judge matrix consistency 
	\lstinputlisting[language=Matlab]{mcode/Judgematrixconsistency.m}
\end{appendices}
\end{document}
%% 
%% This work consists of these files mcmthesis.dtx,
%%                                   figures/ and
%%                                   code/,
%% and the derived files             mcmthesis.cls,
%%                                   mcmthesis-demo.tex,
%%                                   README,
%%                                   LICENSE,
%%                                   mcmthesis.pdf and
%%                                   mcmthesis-demo.pdf.
%%
%% End of file `mcmthesis-demo.tex'.