\section{Memo}
To: The group of Governors From: Team \# 89307 Date: 12 February \\Subject: A Four-State Energy Compact\\
%summarizing the state profiles as of 2009,
%your predictions with regard to energy usage absent any policy changes, and your recommended
%goals for the energy compact to adopt.
Our team has summarized the state profiles as of 2009. Mathematical models are built to illustrate it.\\
In each state, the growth of energy consumption keeps the energy structure from small to large scale, with the proportion of cleaner, renewable energy sources increasing.\\
In New Mexico(the smallest energy consumption), oil and petroleum products, coal and natural gas are the main component.\\
In Texas(the largest energy consumption), oil and petroleum products and natural gas have always dominated. The proportion of biomass and wind energy is very low.\\
We predict the energy consumption of four states by Energy Proportion Model and Growth Rate Model. 
By Energy Proportion Model, the total energy consumption of AZ in 2025 is 2320000, of which 9.4\% is Renewable energy. The most states' proportion of renewable energy is 8\% in 2025.
By Growth Rate Model, the most states' proportion of renewable energy is 9\%.
When it is 2050, the former is 12\%(excluding the data of AZ) while the latter is 11\%.\\
So the results of our models can be referred.
And we find the average price of electricity of the four states in 2025 and 2050 are 35.32732299 and 43.71283002 based on our models.
Therefore, the average price of the four states in 2025 should be set at about 28.26(80\% of the predictive values absent any policy changes) dollars.\\
In 2050 the average price should be set at about 34.97(80\% of the predictive values absent any policy changes) dollars. We state it as the goal for this new four-state energy compact.